cvx-flats

### 2020-05-22 neurips-20/cvx-flats.tex
Taking a pass on Lemma 6 via Lemma 5

\begin{abstract}
%	For finite prediction tasks, one can often naturally model their specific problem with a discrete loss.
%	However, these discrete losses are often hard to optimize, so one often seeks a surrogate losses yielding desirable statistical guarantees with respect to the original problem.
	In prediction tasks, one typically seeks to minimize \emph{empirical risk} by learning a hypothesis function making predictions from a given feature vector about a desired future outcome.
	This hypothesis is learned by minimizing a loss function over a set of labeled training data.
	However, as not all loss functions are easily optimized, one often wishes to optimize a \emph{surrogate loss} yielding the same statistical guarantees as the original.
	In this paper, we are specifically interested in the construction of \emph{consistent} surrogate losses; bonus points if they are ``efficient'' in the dimension of their input.
	We observe a connection between consistent surrogates and indirect property elicitation, which allows us to apply property elicitation complexity results to the minimal dimension of a consistent surrogate.
	We also extend the notion of consistency to properties, so that we may understand when one can construct a convex, consistent surrogate without requiring an original loss.
\end{abstract}

@@

\begin{definition}
  A property $\Gamma:\simplex\to\R$ is \emph{$d$-identifiable} if its level sets are flats of co-dimension at most $d$ intersected with $\simplex$.
  \raft{Update to be consistent with our definitions / notation / conventions.  I'd vote for using co-dimension since it makes so much of the analysis easier...  Could make more formal too.}
  We write $\iden(\Gamma) = \min\{d \in \N : \Gamma\text{ is $d$-identifiable}\}$.
\end{definition}

@@

\jessie{Consider the following four conditions:
\begin{enumerate}
	\item [A] $\zeta:\reals \to \reals_+$ satisfies $\zeta : 0 \mapsto 0$ and is continuous at $0$.
	\item [B] $\epsilon_m \to 0 \implies \zeta(\epsilon_m) \to 0$.
	\item [C] Given $\zeta:\reals \to \reals_+$, for all $u \in \reals^d$, $R_\ell(\psi(u); p) \leq \zeta(R_L(u;p))$.
	\item [D] For all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
\end{enumerate}
$\exists \zeta$ so that $(A \wedge C)$ defines calibration, and we have $A \iff B$ shown in Lemma~\ref{lem:continuous-iff-limits}.  Lemma~\ref{lem:calib-converging-regrets} shoes calibration iff $D$.}

@@

	$\impliedby$ 
\jessie{$D \implies (A \wedge C)$}
	Fix $p \in \simplex$, and consider $\zeta(c) := \sup_{u: R_L(u;p) \leq c} R_\ell(\psi(u); p)$.  
	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above.

\jessie{$D \implies A$, but actually $\lnot B \implies \lnot D$}
Fix $p \in \simplex$.
Suppose we have a sequence $\{\epsilon_m\}$ so that $\epsilon_m \to 0$, but $\zeta(\epsilon_m) \not \to 0$.
If $L$ is continuous over the reals \jessiet{Need this, right?}, then for each $m$, we can construct a subsequence $\{u^j_m\}$ so that $R_L(u^j_m, p) \to \epsilon_m$ for all $m$.
We can now construct the sequence $\{\epsilon'_m\}$ with $\epsilon'_m = \lim_{j \to \infty} R_L(u^j_m, p)$.
This sequence converges to $0$, but we have $\lim_{m \to \infty} \zeta(\epsilon'_m) = \lim_{m \to \infty} \lim_{j \to \infty} \zeta(R_L(u^j_m, p)) \not \to 0$.

%commented out post meeting 05.20.2020
%\jessie{D $\implies$ B ($\iff$ A)}
%	First, we can verify that $\zeta$ as constructed maps $\zeta(0) = 0$ and is continuous at $0$.	
%	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$, which is finite if $\Gamma$ is non-degenerate (i.e. there is no $p \in \simplex$ so that $\Gamma(p) = \emptyset$).
%	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > 0$ (i.e. $\zeta(0) > 0$), then the constant sequence $\{u_m\} = u$ for all $m$ gives $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, yielding a contradiction; therefore, we must have $\zeta(0) = 0$.
%	
%	To see $\zeta$ is continuous at $0$, we just need to show $\lim_{c \to 0^+} \zeta(c) = 0$. 
%	Take any sequence $\{u_m\}$ so that $R_L(u_m; p) \to 0$, and therefore $R_\ell(\psi(u_m);p) \to 0$.
%	Since this is true for all sequences, we have the upper bound tending to $0$, and thus $\lim_{c\to 0^+}\zeta(c) = 0$.
%		
\jessie{D $\implies$ C}
	Now, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by construction of $\zeta$.
	Let $S(v) := \{u' \in \reals^d : R_L(u';p) \leq R_L(v,p) \}$.
	Showing $R_\ell(\psi(u);p) \leq \sup_{u' \in S(u)} R_\ell(\psi(u') ; p)$ for all $u \in \reals^d$ gives the condition $C$.
	As $u$ is in the space over which the surpremum is being taken (as $R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.
\end{proof}

>>>>

\begin{abstract}
%	For finite prediction tasks, one can often naturally model their specific problem with a discrete loss.
%	However, these discrete losses are often hard to optimize, so one often seeks a surrogate losses yielding desirable statistical guarantees with respect to the original problem.
	In prediction tasks, one typically seeks to minimize \emph{empirical risk} by learning a hypothesis function making predictions from a given feature vector about a desired future outcome.
	This hypothesis is learned by minimizing a loss function over a set of labeled training data.
	However, as not all loss functions are easily optimized, one often wishes to optimize a \emph{surrogate loss} yielding the same statistical guarantees as the original.
	In this paper, we are specifically interested in the construction of \emph{consistent} surrogate losses; particularly those that are  ``efficient'' in the dimension of their input.
	We extend the general notion of consistency to properties, so that we may understand when one can construct a convex, consistent surrogate without requiring an original loss, which are uncommon for continuous prediction tasks (for example, the median).
	This allows us to observe that indirect property elicitation is necessary to construct a consistent surrogate, which allows us to apply property elicitation complexity results to the minimal dimension of a consistent surrogate.
	Moreover, when surrogate losses are convex, we state a new lower bound on the dimension of a convex surrogate by using tools from property elicitation.
\end{abstract}

@@

\begin{definition}
  A property $\Gamma:\simplex\to\R$ is \emph{$d$-identifiable} if its level sets are flats of co-dimension at most $d$ intersected with $\simplex$.
  \raft{Update to be consistent with our definitions / notation / conventions.  I'd vote for using co-dimension since it makes so much of the analysis easier...  Could make more formal too.}
  We write $\iden(\Gamma) = \min\{d \in \mathbb{N} : \Gamma\text{ is $d$-identifiable}\}$.
\end{definition}
\jessiet{Flats or unions of flats?}

@@

\jessie{Consider the following four conditions: Suppose we are given $\zeta:\reals_+ \to \reals_+$.
\begin{enumerate}
	\item [A] $\zeta$ satisfies $\zeta : 0 \mapsto 0$ and is continuous at $0$.
	\item [B] $\epsilon_m \to 0 \implies \zeta(\epsilon_m) \to 0$.
	\item [C] Given $\zeta:\reals \to \reals_+$, for all $u \in \reals^d$, $R_\ell(\psi(u); p) \leq \zeta(R_L(u;p))$.
	\item [D] For all $p \in \simplex$ and sequences $\{u_m\}$ so that $R_L(u_m; p) \to 0$, we have $R_\ell(\psi(u_m); p) \to 0$.
\end{enumerate}
$\exists \zeta$ so that $(A \wedge C)$ defines calibration, and we have $A \iff B$ shown in Lemma~\ref{lem:continuous-iff-limits}.  Lemma~\ref{lem:calib-converging-regrets} shoes calibration iff $D$.}

@@

	$\impliedby$ 
\jessie{$D \implies (A \wedge C)$}
	Fix $p \in \simplex$, and consider $\zeta(c) := \sup_{u: R_L(u;p) \leq c} R_\ell(\psi(u); p)$.  
	We will show $R_L(u_m; p) \to 0 \implies R_\ell(\psi(u_m); p) \to 0$ gives calibration via the function $\zeta$ constructed above. 
	With $\zeta$ as constructed, we should that the bound in equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ and apply Lemma~\ref{lem:continuous-iff-limits} to observe that if there is a sequence $\{\epsilon_m\} \to 0$ so that $\zeta(\epsilon_m) \not \to 0$, it is because $R_L(u_m, p) \not \to 0 \not \implies R_\ell(\psi(u_m), p) \to 0$.

\jessie{D $\implies$ C}
Now, we observe that the bound in Equation~\eqref{eq:calibrated-general} is satisfied for all $u \in \reals^d$ by construction of $\zeta$.
Let $S(v) := \{u' \in \reals^d : R_L(u';p) \leq R_L(v,p) \}$.
Showing $R_\ell(\psi(u);p) \leq \sup_{u' \in S(u)} R_\ell(\psi(u') ; p)$ for all $u \in \reals^d$ gives the condition $C$.
As $u$ is in the space over which the surpremum is being taken (as $R_L(u;p) \leq R_L(u;p)$), we then have calibration by definition of the supremum.

\jessie{Not $B$ leads to contradiction of $D$.}
Now suppose there exists a sequence $\{\epsilon_m\} \to 0$ so that $\zeta(\epsilon_m) \not \to 0$.
Consider $S(\epsilon) = \{u \in \reals^d : R_L(u,p) \leq \epsilon\}$.

\begin{align*}
\epsilon_1 \leq \epsilon_2 &\implies S(\epsilon_1) \subseteq S(\epsilon_2)\\
&\implies \zeta(\epsilon_1) \leq \zeta(\epsilon_2)~.~
\end{align*}
Now suppose there exists a sequence $\{u_m\}$ so that $R_L(u_m, p) \to 0$.
Then for all $\epsilon > 0$, there exists a $m' \in \mathbb{N}$ so that $R_L(u_m, p) < \epsilon$ for all $m \geq m'$.
Since this is true for all $\epsilon$, we have $S(\epsilon)$ nonempty for all $\epsilon > 0$, and therefore $\zeta(c)$ is finite for all $c > 0$.
Now if $\zeta(\epsilon_m) \not \to 0$, it must be because $R_\ell(\psi(u_m), p) \not \to 0$ for some sequence converging to zero surrogate regret, and therefore we contradict the statement $R_L(u_m, p) \to 0 \implies R_\ell(\psi(u_m), p) \to 0$.

Moreover, we argue that such a sequence of $\{u_m\}$ with converging surrogate regret always exists by continuity and boundedness from below \jessiet{really just need lower semi-continuity and boundedness from below} of the surrogate loss, since we can take the constant sequence at the (attained) infimum.

%\jessie{$D \implies A$, but actually $\lnot B \wedge C \implies \lnot D$}
%Fix $p \in \simplex$.
%Suppose we have a sequence $\{\epsilon_m\}$ so that $\epsilon_m \to 0$, but $\zeta(\epsilon_m) \not \to 0$.
%If $L$ is continuous over the reals \jessiet{Need this, right?}, then for each $m$, we can construct a subsequence $\{u^j_m\}$ so that $R_L(u^j_m, p) \to \epsilon_m$ for all $m$.
%We can now construct the sequence $\{\epsilon'_m\}$ with $\epsilon'_m = \lim_{j \to \infty} R_L(u^j_m, p)$.
%This sequence converges to $0$, but we have $\lim_{m \to \infty} \zeta(\epsilon'_m) = \lim_{m \to \infty} \lim_{j \to \infty} \zeta(R_L(u^j_m, p)) \not \to 0$. 
%As $R_\ell(\psi(u_m); p) \leq R_L(u_m; p)$ for all $m$, we then have this being true in the limit.
%For this sequence, this then gives a loose bound of $0 \leq \lim_{m\to\infty} R_\ell(\psi(u_m); p) \leq c$.

%commented out post meeting 05.20.2020
%\jessie{D $\implies$ B ($\iff$ A)}
%	First, we can verify that $\zeta$ as constructed maps $\zeta(0) = 0$ and is continuous at $0$.	
%	As $\risk{L}$ and $\risk{\ell}$ are well-defined for all $p \in \simplex$, we note that $\zeta(0) = \sup_{u':R_L(u;p) = 0} (R_\ell(\psi(u'); p)) = \sup_{u' \in \Gamma(p)} (R_\ell(\psi(u'); p))$, which is finite if $\Gamma$ is non-degenerate (i.e. there is no $p \in \simplex$ so that $\Gamma(p) = \emptyset$).
%	If there is a $u \in \Gamma(p)$ so that $R_\ell(\psi(u); p) > 0$ (i.e. $\zeta(0) > 0$), then the constant sequence $\{u_m\} = u$ for all $m$ gives $R_L(u_m;p) \to 0$ but $R_\ell(\psi(u_m); p) \not \to 0$, yielding a contradiction; therefore, we must have $\zeta(0) = 0$.
%	
%	To see $\zeta$ is continuous at $0$, we just need to show $\lim_{c \to 0^+} \zeta(c) = 0$. 
%	Take any sequence $\{u_m\}$ so that $R_L(u_m; p) \to 0$, and therefore $R_\ell(\psi(u_m);p) \to 0$.
%	Since this is true for all sequences, we have the upper bound tending to $0$, and thus $\lim_{c\to 0^+}\zeta(c) = 0$.
%
